---
title: "Options"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Options}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(billboard)
library(dplyr)
```

`billboard` comes with countless options, they are **not** all listed here. This page merely tries to demonstrate what can be achieved with the package. 

### Labels & orientation

Add labels and rotate the chart and add a title.

```{r}
library(dplyr)

mtcars %>% 
  mutate(models = rownames(.)) %>% 
  slice(1:5) %>% 
  b_board(models) %>% 
  b_bar(wt) %>% 
  b_rotate() %>% 
  b_labels() %>% 
  b_title("Rotated chart")
```

### Legend

Change the legend square size and position. Note that you can name each chart added with `name`

```{r}
mtcars %>% 
  mutate(models = rownames(.)) %>% 
  slice(1:5) %>% 
  b_board(models) %>% 
  b_bar(wt, name = "weight") %>% 
  b_bar(drat) %>% 
  b_legend(width = 50, height = 20, position = "inset")
```

### Empty

No axis change or legend, change height.

```{r}
mtcars %>%
  mutate(x = 1:n()) %>% 
  b_board(x) %>% 
  b_spline(wt) %>% 
  b_xaxis(show = FALSE) %>% 
  b_yaxis(show = FALSE) %>% 
  b_size(height = 50) %>% 
  b_legend(show = FALSE)
```

### Mark

Mark lines and regions.

```{r}
mtcars %>% 
  mutate(x = 1:n()) %>% 
  b_board(x) %>% 
  b_area_spline(drat, name = "Rear axle ratio") %>% 
  b_spline(mpg, axis = "y2") %>% 
  b_grid_line(3, "avg (maybe)", axis = "y") %>% 
  b_region("x", 8, 12)
```

### Color

Customise chart color.

```{r}
mtcars %>% 
  mutate(x = 1:n()) %>% 
  b_board(x) %>% 
  b_bar(wt) %>% 
  b_area(drat) %>% 
  b_bar(mpg, axis = "y2") %>% 
  b_color_brewer("Accent", 3)
```

### Subchart

Add a subchart

```{r}
mtcars %>% 
  mutate(x = 1:n()) %>% 
  b_board(x) %>% 
  b_bar(wt) %>% 
  b_area(drat) %>% 
  b_subchart()
```
